---
title: "Developing Data Products - Final Project"
author: "Zaid Muhsin"
date: "December 15, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r}
setwd("C://data_science/09_data_product/project")
population<-read.csv("census_new_zealand.csv")
```

## Backgrouond

As part of the coursera course (Developing Data Product), students required to develop a shiny application in R. 

The developed application chosen for this project, plots the New Zealand population by gender since 1971, using the ggplot.

Data had been downloaded from http://archive.stats.govt.nz/Census 

## Shiny App

The shiny app meet the below requirement.

The application meets the following requirements:

 - Some form of input (widget: radio button, list box )
 - Some operation on the ui input in sever.R
 - Some output displayed as a result of server calculations (plotting the graph using ggpplot).
 - You must also include enough documentation so that a novice user could use your application.

The application allows the user to choose the gender, and the year.
Colour of the plot changes dynamically based on gender  (blue for men and pink for female).

## Data Used

```{r, comment = "", echo=TRUE}
head(population)
```    

##Uploads

1. The shiny app was published into shinyapps.io
https://zmuhs.shinyapps.io/Develop_Data_Product_Project/

2. The codes (server.R and ui.R) been uploaded into github.
https://github.com/zmuhs/Develop_Data_Product_Project



